HGIS 2021-05-28 Carbonates

### 2021-06-16 inst/rmd/HGIS_pendleton_2021-05-28.Rmd
Add comparison to graphite

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, echo = FALSE)
```

@@

```{r}
df <- process_hgis_results(file, date, standards)
write_csv(df, here("data_analysed/HGIS_2021-05-28_raw.csv"))
write.xlsx(df, here("data_analysed/HGIS_2021-05-28_raw.xlsx"))
```

@@

write_csv(df_sum, here("data_analysed/HGIS_2021-05-28_results.csv"))
write.xlsx(df_sum, here("data_analysed/HGIS_2021-05-28_results.xlsx"))
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

@@

```{r}
df <- process_hgis_results(file, date, standards)
#write_csv(df, here("data_analysed/HGIS_2021-05-28_raw.csv"))
#write.xlsx(df, here("data_analysed/HGIS_2021-05-28_raw.xlsx"))
```

@@

# write_csv(df_sum, here("data_analysed/HGIS_2021-05-28_results.csv"))
# write.xlsx(df_sum, here("data_analysed/HGIS_2021-05-28_results.xlsx"))
```

@@

## Agreement with graphite

Agreement of Haiti core samples. Graphite samples were pretreated with HCl to leach 30% of the sample. HGIS samples not pretreated.

Load Simon's data and compare

```{r}
haiti <- filter(df_sum, str_detect(sample_name, "HATC1")) %>% 
  mutate(rec_num = case_when(pos == 14 ~ 171989,
                             pos == 15 ~ 171995,
                             pos == 16 ~ 171999))

graphite_results <- getRecOS(c(171999,171995,171989)) %>% 
  select(rec_num, fm_corr = f_modern, sig_fm_corr = f_ext_error)

combined_results <- haiti %>% 
  select(sample_name, rec_num, fm_corr, sig_fm_corr) %>% 
  left_join(graphite_results,
            by = "rec_num", 
            suffix = c("_hgis", "_graphite")) %>% 
  mutate(fm_diff = fm_corr_graphite - fm_corr_hgis,
         fm_mean = mean(c(fm_corr_hgis, fm_corr_graphite))) %>% 
  pivot_longer(c(fm_corr_graphite, sig_fm_corr_graphite, 
                 fm_corr_hgis, sig_fm_corr_hgis), 
               names_to = c(".value", "method"),
               names_pattern = "(.*)_(.*)") %>% 
  mutate(fm_diff = fm_corr - fm_mean)

combined_results %>% 
  select(sample_name, rec_num, method, fm_corr, sig_fm_corr) %>% 
knitr::kable()
```

Difference plot

```{r}
combined_results %>% 
  ggplot(aes(fm_corr, fm_diff, color = method, shape = method)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr)) +
                  #position = position_dodge2(width = 0.05, padding = 0.1)) +
  ylim(-0.02, 0.02) +
  labs(title = "Haiti Core Graphite vs HGIS",
       x = "Fraction modern",
       y = "Fm - mean Fm") + theme_classic()
```
